\documentclass[./dissertation.tex]{subfiles}
\begin{document}

\chapter{Related Work}

\section{Learning Success Models for Grasping}
Robotic grasping is a major area of study within robotics due to its wide use in manipulation tasks. A significant portion of research focused on robotic grasping has employed the use of learning methods, several of which include the learning of a grasp success model. These models are used to predict the success of certain gripping actions with state information from RGB images, object positions, or affordance representations. After collecting data from 50,000 grasp attempts, \cite{SSS} trained a Convolutional Neural Network (CNN) to take image patches as input and output the probability of grip success for candidate grasp angles. Similarly, \cite{LevineGrasp} learned a grasp prediction network that predicts the likelihood of a successful grasp and integrated this estimate in a continuous servo controller. After generating a dataset of synthetic point clouds, \cite{DexNet} learned a grip robustness function that scores candidate grasps and enables planning by selecting the highest rated action. Other methods, such as \cite{DSGD} and \cite{detry2011learning}, learn these grasp success models and utilize them for simple evaluation or to find high success actions. The method in this paper follows this line of work by learning a grasp success model that maps states and actions to success probabilities. The learned success predictor in this work is interpreted as a reward function, and utilized to learn an effective grasping policy.  

\section{Offline Reinforcement Learning}
Offline Reinforcement Learning \cite{OfflineRLSurvey} learns a policy $\pi_\mathcal{D}$ from a fixed dataset collected by an exploration policy $\pi_\text{Explore}$ without further environment interaction. Unlike other learning methods that employ the use of training datasets, the goal of Offline RL is the same as standard Online RL, which is to learn a policy that maximizes expected reward. Because training is performed on static, batched data, Offline RL can be more sample-efficient and optimize faster than Online RL. However, a central challenge with Offline RL is distribution shift: the learned policy $\pi_\mathcal{D}$ may end up in states or take actions during training that are not present in the dataset, which can lead to unreliable value estimation. To address this issue, prior work employs techniques such as importance sampling \cite{IS}, regularization\cite{Offline2}, and policy constraints \cite{Offline1}. Although the method in this paper incorporates offline training, it is not pure Offline RL because the learned policy $\pi_\mathcal{D}$ is subsequently deployed to acquire more data and iteratively improve the reward model for further offline training. Despite this, it is worth to note that regularization, an Offline RL technique, formed a primary inspiration for this approach.

\section{Model-Based Reinforcement Learning}
Model-Based Reinforcement Learning \cite{MBRLSurvey} is the process of learning an environment dynamics or transition function and leveraging this model for policy optimization. The learned transition model allows policies to be simulated by predicting the resulting state of actions, reducing the need for costly real-world interactions. This leads to improved sample efficiency, especially in settings where data collection is expensive or time consuming. The main problem with Model-Based RL is model accuracy and the uncertainty induced by model errors. Several approaches address this issue through uncertainty-aware modeling, such as ensemble methods. For example, \cite{MBRL1} trains an ensemble of $K$ dynamics models and chooses one randomly for rollouts, while \cite{MBRL2} learns $N$ reward models and estimates the reward as the ensemble mean penalized by the maximum standard deviation. In addition to this, many Dyna-style \cite{Dyna} methods implement iterative model improvement to continuously refine their model. Both \cite{MBRL3} and \cite{MBRL4} follow this paradigm by alternating between model learning and data collection with the optimized policy to progressively improve performance. Although the proposed approach is related to Model-Based RL, it does not explicitly model a transition function. Instead, only the reward model is learned and used to optimize the policy. Despite this distinction, the method adopts ideas from Model-Based RL, including ensemble networks and iterative model improvement.

% \subsection{Inverse Reinforcement Learning}
% Much like in Inverse Reinforcement Learning, a reward model $\hat{r}(s,a)$ is learned from data. However, the assumption in Inverse Reinforcement Learning is that the data is exclusively that collected from an expert policy $\pi^{Expert}$. This method combines data collected from expert demonstrations and that from random exploration. In addition to this, data is generally unlabeled when implemented in Inverse Reinforcement Learning, as it is assumed to be trajectories from an expert. The data utilized in this paper, however, is labeled with the observed reward. Despite the similarities to Inverse Reinforcement Learning, the two distinctions above set this method apart from being categorized in this way. 

% \subsection{Robust Reinforcement Learning}
% Reinforcement learning is being increasingly applied to real-world tasks, where uncertainty is inherent to the environment. One way to tackle uncertainty is with robust RL, which optimizes with the worst-case transition function from the set of possible transition functions.    The goal of Robust RL is to produce a policy that has high expected reward while also having the ability to handle uncertain environments. The goal of the modified objective in this paper is to also handle uncertainty, but it is done so in a much different way. Still, the method in this paper draws a lot from the ideas of Robust RL

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


    % \chapter{All about Citations and BibTex}
    % Before diving into BibTex and how it all works, citing a figure or table that does not exist in the same subpage is also possible. Figure ~\ref{fig:digilogo} is on page ~\pageref{fig:digilogo}.
    % \section{The Bibliography}
    %   In this section, we are going to dive into how LaTeX automates your citations and generates your bibliography on the fly. That way if you make any additions or deletions, LaTeX will handle all of that.
    %   \subsection{BibTex File Formatting}
    %     All of the citations will live in one file, in this case is called dissertation.bib. This file will have to follow a specific format. Each entry will start with an @ and following the type of entry. If it is a book, then it will start with @book\{...\}. Inside the brackets will contain all of the information about this entry. Fisrt it will have an ID that you will use to cite inside the tex files. Not sure of a convention, but each ID must be unique so something that pertains to the entry should suffice. There is a lot you can put with each entry, so \href{https://www2.cs.arizona.edu/~collberg/Teaching/07.231/BibTeX/bibtex.html}{here} is a link to all the different types and the different attributes each entry can have. Each attribute inside the curly brackets needs to be separated by a comma, but each entry just needs to be on its own line and not separated by a comma.
    %   \subsection{Loading BibTex File}
    %     If you look at the main file, \textit{disseration.tex}, there are two places that involve the bibliography. First is at the top where the command is \verb+\usepackage[backend=biber,style=apa,sorting=nyt]{biblatex}+. This lets you change the style and how the bibliography is sorted. Don't touch the \textit{backend=biber}. The next command is \verb+\addbibresource{dissertation.bib}+ further down before the actual document begins. This does not neet to be touched because it also needs to be called the same as the main file, besides the extention. This is how the compiler knows which file to grab.

    %     Then lets take a look at the very bottom of \textit{dissertation.tex}, there will be two commands that are very important.
    %     \begin{verbatim}
    %       \addcontentsline{toc}{chapter}{Bibliography}
    %       \printbibliography[title={Bibliography}]
    %     \end{verbatim}
    %     Unless you want to change the title of the bibliography or sort the bibliography, then you may want to touch this. Other than that, there is no need to mess with these two lines of the file.

    % \section{Inline Citations}
    % There are two commands that you will need to know. \verb+\cite & \parencite+. The way these are used is when you use these commands, you need to have provide the ID of the specific entry in the bib file. \verb+\cite{TD3}+ produces \cite{TD3} where as the other command adds parentheses around it. These will change when you change the style of the Bibliography from apa to mla or any other format.
    % \parencite{TD3}

\end{document}
